### 2020-06-30 chapters/validation.tex
More visualizations

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/merchant-x5-reference.png}
      \caption{Merchant feature x5 reference time-series}
      \label{fig:merchant-x5-reference}
    \end{center}
\end{figure}

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/merchant-x5-target.png}
      \caption{Merchant feature x5 target time-series}
      \label{fig:merchant-x5-target}
    \end{center}
\end{figure}

%This merchant and in particular these datasets were known to suffer a lot from concept drift. Our system produced a large list of alerts. We had alerts from nearly the beginning of the target period until the end.

%low drift:
    %x1 - max_amt_rate_per_location_72h
    %x2 - num_preauths_per_card_1w
    %x3 - user_avg_amount_completions_1h
    %x4 - completions_rate_per_location_zip3_72h

%high drift:
    %x5 - completion_rate_per_card_72h

%Due to the large number of features (183) we only show the plots and visualizations drawn for some. Furthermore, we refer to features with anonymized identifiers, like our example feature, x1. Figure \ref{fig:merchant-x1-corrected-pvalues} shows the corrected p-values (Formula \ref{for:corrected-pvalue}) for feature x1 at for each event of the time-series and Figure \ref{fig:merchant-x1-corrected-pvalues-zoom} provides a closer look on the region where the p-values drop below the threshold (FWER = 1\%).

>>>>

This merchant and in particular these datasets were known to suffer a lot from concept drift. Our system produced a large list of alerts, from nearly the beginning of the target period until the end. Due to the large number of features (183) we only show some plots. Furthermore, we refer to features with anonymized identifiers, like feature $x_t$. In the following plots, we show the corrected p-values (Formula \ref{for:corrected-pvalue}) for some features at each event of the time-series and the FWER threshold set at 1\%. A feature is considered divergent at a given timestamp if below that threshold line.

%feats = [max_amt_rate_per_location_72h, num_preauths_per_card_1w, user_avg_amount_completions_1h, completions_rate_per_location_zip3_72h, completion_rate_per_card_72h]
%low drift:
    %x1 - max_amt_rate_per_location_72h
    %x2 - num_preauths_per_card_1w
    %x3 - user_avg_amount_completions_1h
    %REMOVED %x4 - completions_rate_per_location_zip3_72h
%high drift:
    %x4 - completion_rate_per_card_72h

@@

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/merchant-x1-correctedpvalues.png}
      \caption{Merchant feature x1 corrected p-values}
      \label{fig:merchant-x1-correctedpvalues}
    \end{center}
\end{figure}

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/merchant-x2-correctedpvalues.png}
      \caption{Merchant feature x2 corrected p-values}
      \label{fig:merchant-x2-correctedpvalues}
    \end{center}
\end{figure}

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/merchant-x3-correctedpvalues.png}
      \caption{Merchant feature x3 corrected p-values}
      \label{fig:merchant-x3-correctedpvalues}
    \end{center}
\end{figure}

\begin{figure}[!htb]
    \begin{center}
      \includegraphics[scale=0.5]{figures/merchant-x4-correctedpvalues.png}
      \caption{Merchant feature x4 corrected p-values}
      \label{fig:merchant-x4-correctedpvalues}
    \end{center}
\end{figure}
